M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-05-19 notes/thesis-latex-template/thesis.tex
Update "Summary of achievements" in the introduction chapter.

\section{Objective of this work}

The goal of this work is to develop and implement a software toolbox 
for the generation of iterative numerical solvers for nonlinear macroscale 
electrokinetic problems, and to apply it to the study
of systems that have no closed-form solutions, 
such as ion-exchanger migration \cite{yariv2010migration} 
and the electrophoresis problem \cite{schnitzer2012surface}.
This solver can be used to gain insight into the chemical 
and physical behavior in far more general regimes than 
are currently well-understood, 
and also to possibly lead to further analytical developments, 
based on new scaling behavior
discovered numerically. 
We may also target interesting physical
phenomena that have been observed experimentally.
One such phenomenon is nonlinear electrokinetic vortex flow, 
which is useful for microfluidic mixing applications 
\cite{wang2004mix, ben2002vortex}.

@@

In conclusion, the main contribution of this work is the development 
of a numerical framework for solving nonlinear coupled PDE steady-state systems, 
with application to electrokinetic problems such as ion-exchanger migration and 
particle electrophoresis, and asymptotic analytical verification of the results.

>>>>

\section{Summary of achievements in this work}

In this work, we develop and implement a novel software framework, that enables the generation of iterative numerical solvers for nonlinear macroscale electrokinetic problems, with the boundary layer replaced by nonlinear analytical boundary conditions.
We apply this framework to the study of systems that have no closed-form solutions, such as ion-exchanger migration \cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
The numerical results of the can be used to gain insight into the chemical and physical behavior in far more general regimes than are currently well-understood, and also to possibly lead to further analytical developments, based on new scaling behavior that is discovered numerically.
We have also discovered interesting physical phenomena that may be observed experimentally. One such phenomenon is nonlinear electrokinetic vortex flow, which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex}.
In addition, we develop and present an asymptotic derivation for the ion-exchanger migration problem up to the third order terms. This new analytical result is also used to verify the numerical framework and the obtained numerical results.

@@
